%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {\normalsize Software Engineer} % Job title
    {\Large Adaptive Autosar | PES8 | VECTOR Informatik . Contract} % Organization
    {\normalsize Stuttgart, Germany} % Location
    {\normalsize Apr. 2023 - Present} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\normalsize Integrating and Deployment of Adaptive MICROSAR into Customer Projects Like Mercedes Benz and STLA Group.}
        \item {\normalsize Consulting and Supporting our Customers in topics concerning architecture, implementation and integration.}
        \item {\normalsize Experienced in Configuration Features in Adaptive MICROSARModules .}
        \item {\normalsize Modeling Features in Adaptive MICROSAR Stacks Like Communication Services, Diagnostics Services and create Adaptive application following Autosar methodology .}
        \item {\normalsize Debugging and troubleshooting all Reported Bugs in Adaptive Microsar including Communications/Diagnostics or related Os Behavior Specially Qnx and Linux system.}
        \item {\normalsize Analyzing Qnx System using momentics and Qnx Command line to understanding system manar.}
        \item {\normalsize Staying on the Cutting edge of technology e.g New Feature in Adptive MICROSAR.}
        \item {\normalsize Participated in Mercedes Projects in multiple Workshops.}
        \item {\normalsize Working in Agile Environments.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {\normalsize Standard Software Engineer} % Job title
    {\Large Classic Autosar | V-Core | Valeo} % Organization
    {\normalsize Cairo, Egypt} % Location
    {\normalsize Oct. 2021 - Apr. 2023} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\normalsize Responsible for analyzing and implementing software requirements.}
        \item {\normalsize Integrating, Configuring and testing of AUTOSAR stacks (Diagnostic, Communication, Memory, Mode management, Network management).}
        \item {\normalsize Good knowledge in configuration and integration and testing of Autosar Ethernet Stack.}
        \item {\normalsize Understanding of UDS protocol [ISO 14229-1].}
        \item {\normalsize Apply standard software guidelines at components Implementation including MISRA-C rules and Valeo naming rules.}
        \item {\normalsize Good knowledge of AUTOSAR E2E Specially VW E2E.}
        \item {\normalsize Automating the configuration, Testing, and merging different packages using Vector tools or Python scripts.}
        \item{\normalsize A-SPICE L2 deployment.}
        \item {\normalsize Understanding of Agile workflow.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {\normalsize Intern Software Engineer} % Job title
    {\newline \Large Adaptive Autosar | Geeds | Valeo} % Organization
    {\normalsize Cairo, Egypt} % Location
    {\normalsize Nov. 2020 - Aug. 2021} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\normalsize Good knowledge of Adaptive Autosar Workflow (development, integrating, Deployment).}
        \item {\normalsize Understanding of Service-oriented Architecture Concepts.}
        \item {\normalsize Good Knowledge of service UCM sub-module, Centralized service UCM-Master and Fundamental Stack(ara::Com, ara::EXEC).}
        \item {\normalsize Good knowledge of Yocto Project, Qemu, and Posix.}
        \item {\normalsize Good knowledge of Linux commands and OS basic concepts.}
        \item{\normalsize Good knowledge of SOME/IP.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {\normalsize Intern Electronics Engineer} % Job title
    {\newline \Large Electronics | MasterTechCo.} % Organization
    {\normalsize Alexandria , Egypt} % Location
    {\normalsize JUL. 2020 - Sep. 2020} % Date(s)
    {\setstretch{1.25}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\normalsize Restructured some machine-like CNC, shellers, servers, Cico Centrals, Cico cell phones, and machine drivers}
        \item{\normalsize Trained on how to design relevant circuits for ECUs.}
        \item{\normalsize Implemented power supplies for small and critical control circuits.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
{\normalsize Intern DevOps Engineer} % Job title
{\newline \Large Automation | Sprints | Mentorship by Vodafone UK} % Organization
{\normalsize Cairo , Egypt} % Location
{\normalsize JUL. 2020 - AUG. 2020} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{\normalsize Trained on new technology to CI/CD.}
    \item{\normalsize Used tools like Docker, Git, Jenkins, and bash scripts.}
    \item{\normalsize Implemented a CI/CD cycle for features on the develop branch in Sprints School Platform.\newline}
  \end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
