%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{\normalsize Automotive Project} % Role
{\Large IDC Project Mercedes Benz} % Event
{\normalsize Stuttgart, Germany} % Location
{\normalsize Nov. 2023 - Present} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {Integrating and Testing all IDC Applications to New Adaptive Platform Delivered from Vector.}
    \item {Analysing and Adapting all Patches applied over Vector Delivery and fixing any new produced issue.}
    \item {Testing all integrating Systems by checking the system behavior for all Variants before and after integration then creating an analysis page with all new features delivered in the last release.}
    \item {Debugging and Fixing any Bugs related to adaptive Microsar or applications.}
    \item {Supporting customer teams in issue/understanding related to Microsar Adaptive.}
    \item {Participated in Multiple Workshops and Debugging sessions with different MB teams.}
    \item {Sharing Knowledge for all new features and also Tips and Tricks relating to troubleshooting in Qnx or Adaptive Microsar.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize Automotive Project} % Role
{\Large RTCU Project STLA Groups} % Event
{\normalsize Stuttgart, Germany} % Location
{\normalsize Apr. 2023, Nov. 2023} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {Migrating and Deployment Microsar Project based on TACO CMake to be Compatible with Yocto and creating qemuarm image based on arm32-bit.}
    \item {Supporting Customer to create almost Diagnostics services in Adaptive MICROSAR.}
    \item {Supporting Customer to Adapting the Modelling and DEXT to be Compatible with new MICROSAR versions.}
    \item {Participated in STLA Projects for Multiple Debug sessions related to building or implementing new features or inventing new workarounds to running the system instead of using Execution manager using Linux system.}
    \item {Implementing a solution to call Taco CMake through Yocto Recipe to Build Adaptive Microsar.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize Automotive Project} % Role
{\Large P2 VW Projects} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Mar. 2022, Apr. 2023} % Date(s)
{\setstretch{1.25}
  \begin{cvitems} % Description(s)
    \item {Developed E2E Handler to meet VW Requirements Specifications and Tested it.}
    \item {Integrate Lin Protocol as Slave and Create whole Simulated system for testing.}
    \item {Implemented and Configure Several Diagnostics services and handling with Memory management.}
    \item {Implemented Ecu Hard and Soft reset Especially for VM Specifications.}
    \item {Implemented General Test cases for the whole system including implemented feature.}
    \item {Developed VM Knock-Out Component Feature for ECU and Communication.}
    \item {Design the applications and Handlers then integrate them with the whole architecture.}
    \item {Integrate my Platform with applications team.}
  \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize Architecture Project} % Role
{\Large Automated Integration (VALEO MARS)} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize May. 2022, Apr. 2023} % Date(s)
{\setstretch{1.25}
    \begin{cvitems} % Description(s)
        \item {\normalsize Developed automation way called Buttom-UP Approach with Building Units. }
        \item {\normalsize Developed Python scripts to integrate Platform with Specific Components also with Specific OEM Profile as per Manifest Have several input needs, then integrate my automation Scripts to CI and also Unified IDE and Whole Valeo Software Branches used it and that is for the easiest way to make sure that whole integrated feature doesn't have any warning or issues or workarounds also tested as Per OEM Profile, also reduce wasted times of integrating sample Platforms, also the increasing the varieties of Features that could be added without human interfere.}
    \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize Automotive Project} % Role
{\Large P2 Daimler Project (Artemis)} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Oct. 2021, Apr. 2023} % Date(s)
{\setstretch{1.25}
      \begin{cvitems} % Description(s)
        \item {\normalsize Implemented Test Cases for covering all general Requirements for Mbbl Platform. }
        \item {\normalsize Develop General Test Case and Develop ECU Extract Parser tool to extract all info and test against the system configurations.}
        \item {\normalsize Configure several Diagnostics services and Link them to our Handling Component through RTE.}
        \item {\normalsize Configure Network Management to fit MB Requirements Specifications and test it.} 
        \item {\normalsize Integrate XCP to The system.} 
      \end{cvitems}
}  
%---------------------------------------------------------
\cventry
{\normalsize Graduation Project Mentorship by Valeo} % Role
{\Large Update And Configuration Management in Adaptive Autosar Platform} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize Dec. 2021, JUL.2021} % Date(s)
{\setstretch{1.25}
      \begin{cvitems} % Description(s)
        \item {\normalsize Implemented a system that ensures robust, fail-safe, and secure OTA updates.}
        \item {\normalsize Developed UCM, UCM MASTER, Driver Application, OTA Client, OTA Server, and OTA Website.}
        \item {\normalsize Developed Update And Configuration Management Subordinate Release 19/11 to meet software specifications of Autosar organization Release 20/11.}
        \item {\normalsize Implemented Update And Configuration Management Master as Centralized service over SOME/IP that orchestrates the multiple UCMs in different nodes in a network of vehicles and control update campaign flow to All UCMs Subordinate.}
        \item{\normalsize Implemented OTA Client as an Application in communication with the backend to fetch vehicle packages that needed to update and Polling of an update is available.}
        \item{\normalsize Implemented Driver Application to request a transfer, process, or activation permission from the vehicle driver and Notify the vehicle driver of safety and security measures he has to apply to the vehicle to proceed to the next step into the update campaign.}
        \item{\normalsize Built Image and SDK for Raspberry Pi 3 to Support QT5, SSH,Wifi, and Ethernet that are not compatible with Release 19/11.}
      \end{cvitems}
}
%---------------------------------------------------------
\cventry
{\normalsize CI/CD Project} % Role
{\Large Automation Projects} % Event
{\normalsize Cairo, Egypt} % Location
{\normalsize MAY. 2021, AUG.2021} % Date(s)
{\setstretch{1.25}
      \begin{cvitems} % Description(s)
        \item {Implemented Docker and Jenkins files to deploy a simple web Django app on the local host machine as a part of the sprints training.}
      \end{cvitems}
}  
%---------------------------------------------------------
\end{cventries}
